\texttt{SuperScreen}: An open-source package for simulating the magnetic response of two-dimensional superconducting devices

### 2021-11-20 main.tex
Updates from Overleaf

\newcommand{\inline}[1]{\mintinline{python}{#1}\xspace}
\newcommand{\SuperScreen}{\inline{SuperScreen}}
\newcommand{\um}{\mu\mathrm{m}}

@@

\begin{code}
\begin{minted}[fontsize=\small]{python}
# Create a device representing square thin film.
device = sc.Device(
    "film",
    layers=[sc.Layer("base", Lambda=0, z0=0)],
    films=[sc.Polygon("film", layer="base", points=sc.geometry.box(20))],
    length_units="um",
)
device.make_mesh(min_triangles=8000)
# Specify the vortex position.
vortices = [sc.Vortex(x=0, y=0, layer="base")]
# Sweep Lambda, solve the model, and evaluate the field at the given coordinates.
Lambdas = np.linspace(0, 2, 5) # [device.length_units]
for Lambda in Lambdas:
    device.layers["base"].Lambda = Lambda
    solution = sc.solve(device=device, vortices=vortices)[-1]
    # Use solution.field_at_position() to evaluate the magnetic field profile,
    # and solution.polygon_fluxoid() to calculate fluxoids.
\end{minted}
\captionof{listing}{Creates a square superconducting film with side length $20\,\um$ and calculates the magnetic field distribution near a vortex at the center of the film as a function of the the effective penetration depth, $\Lambda$ (see Figure~\ref{fig:pearl}).}
\label{code:pearl-vortex}
\end{code}

@@

\begin{table*}[]
\centering
\begin{tabular}{|l|l|l|}
\hline
Layer name        & Thickness [nm] & Films located in layer \\ \hline
\hline
BE (bottom) & 160            & Field coil, pickup loop shield      \\ \hline
I1          & 150            & ---                                 \\ \hline
W1          & 100            & Pickup loop, field coil shield      \\ \hline
I2          & 130            & ---                                 \\ \hline
W2 (top)    & 200            & Pickup loop shield, modulation coil \\ \hline
\end{tabular}
\caption{Layer stackup for the SQUID susceptometers Section~\ref{section:examples:scanning-squid}. See Ref.~\cite{Kirtley2016-zz} for more details on the designed of the suscpetometers.}
\label{table:squid-layers}
\end{table*}

@@

The limitation described above can be seen in the model of the largest SQUID susceptometer described in Section~\ref{section:examples:scanning-squid}, which has a field coil inner radius of $6\,\um$ and a total modeled area of roughly $600\,\um^2$. As shown in Figure~\ref{fig:xlarge-dz-dr}, \SuperScreen significantly underestimates the mutual inductance between the field coil and pickup loop when $\delta z <\delta r$ because, in that case, the discretized version of Eq.~\ref{eq:hz-from-kernel} does not correctly compute the magnetic field due the stream function in the superconducting layers. For the sake of computing mutual inductance as in Section~\ref{section:examples:scanning-squid}, it is physically reasonable to artificially increase the vertical spacing between layers such that $\delta z\geq \delta r$ because we expect the magnetic field a vertical distance $\delta z$ away from the center of the field coil to fall off roughly as $\left(\delta z^2 + R^2_\mathrm{FC}\right)^{-3/2}$, where $R_\mathrm{FC}\approx 6\,\um\gg\delta z$. However, in situations where $\delta z$ is a critical dimension (in the sense that increasing it invalidates the physical model), one's only option is to decrease $\delta r$ by increasing the density of the mesh.

For this reason, mutli-layer structures with closely-spaced layers are the most challenging class of problem to solve. The iterative method used described in Section~\ref{section:model:multilayer} is memory-intensive for models with a large mesh (many vertices $p$ and triangles $t$, with typically $p\approx t / 2$) and/or many layers $L$. The average distance between vertices decreases slowly with increasing number of triangles, $\langle\delta r\rangle\sim t^{-1/2}$, whereas the size of the (dense floating-point) $p\times t$ matrix that represents the dipole kernel $Q_z(\vec{r},\vec{r}')$ in Eq.~\ref{eq:hz-from-kernel} increases roughly as $t^2$. The end result is that the memory footprint of kernel matrix scales roughly as $\langle\delta r\rangle^{-4}$, so decreasing the mean distance between vertices by a factor of 2 increases the memory required by a factor of 16. Furthermore, for a model with $L$ layers there are $\binom{L}{2} = L(L-1)/2$ such kernel matrices needed for each iteration of the calculation outlined in Section~\ref{section:model:multilayer}. In \inline{superscreen.solve()}, these $\binom{L}{2}$ matrices are computed during the first iteration and then cached in memory for use in subsequent iterations. One can force the kernel matrices to be cached to disk if they would otherwise occupy too large a fraction of the available system memory using the \inline{cache_kernel_memory_cutoff} argument, but this comes at a significant performance cost.

>>>>

\newcommand{\inline}[1]{\mintinline{python}{#1}\xspace}
\newcommand{\SuperScreen}{\inline{SuperScreen}}
\newcommand{\um}{\mu\mathrm{m}}
\newcommand{\nm}{\mathrm{nm}}

@@

\begin{code}
\begin{minted}[fontsize=\small]{python}
# Create a device representing square thin film.
device = sc.Device(
    "film",
    layers=[sc.Layer("base", Lambda=0, z0=0)],
    films=[sc.Polygon("film", layer="base", points=sc.geometry.box(20))],
    length_units="um",
)
device.make_mesh(min_triangles=8_000)
# Specify the vortex position.
vortices = [sc.Vortex(x=0, y=0, layer="base")]
# Sweep Lambda, solve the model, and evaluate the field at the given coordinates.
Lambdas = np.linspace(0, 2, 5) # [device.length_units]
for Lambda in Lambdas:
    device.layers["base"].Lambda = Lambda
    solution = sc.solve(device=device, vortices=vortices)[-1]
    # Use solution.field_at_position() to evaluate the magnetic field profile,
    # and solution.polygon_fluxoid() to calculate fluxoids.
\end{minted}
\captionof{listing}{Creates a square superconducting film with side length $20\,\um$ and calculates the magnetic field distribution near a vortex at the center of the film as a function of the the effective penetration depth, $\Lambda$ (see Figure~\ref{fig:pearl}).}
\label{code:pearl-vortex}
\end{code}

@@

\begin{table*}[]
\centering
\begin{tabular}{|l|l|l|}
\hline
Layer name        & Thickness & Films located in layer \\ \hline
\hline
BE (bottom) & $d_\mathrm{BE} = 160\,\nm$            & Field coil, pickup loop shield      \\ \hline
I1          & $d_\mathrm{I1} = 150\,\nm$            & ---                                 \\ \hline
W1          & $d_\mathrm{W1}=100\,\nm$            & Pickup loop, field coil shield      \\ \hline
I2          & $d_\mathrm{I2} = 130\,\nm$            & ---                                 \\ \hline
W2 (top)    & $d_\mathrm{W2} = 200\,\nm$            & Pickup loop shield, modulation coil \\ \hline
\end{tabular}
\caption{Layer stackup for the SQUID susceptometers Section~\ref{section:examples:scanning-squid}. See Ref.~\cite{Kirtley2016-zz} for more details on the designed of the suscpetometers.}
\label{table:squid-layers}
\end{table*}

@@

The limitation described above can be seen in the model of the largest SQUID susceptometer described in Section~\ref{section:examples:scanning-squid}, which has a field coil inner radius of $6\,\um$ and a total modeled area of roughly $600\,\um^2$. As shown in Figure~\ref{fig:xlarge-dz-dr}, \SuperScreen significantly underestimates the mutual inductance between the field coil and pickup loop when $\delta z <\delta r$ because, in that case, the discretized version of Eq.~\ref{eq:hz-from-kernel} does not correctly compute the magnetic field due the stream functions of the superconducting layers. For the sake of computing mutual inductance as in Section~\ref{section:examples:scanning-squid}, it is physically reasonable to artificially increase the vertical spacing between layers such that $\delta z\geq \delta r$ because we expect the magnetic field at the pickup loop, a vertical distance $\delta z$ away from the center of the field coil, to fall off roughly as $\left(\delta z^2 + R^2_\mathrm{FC}\right)^{-3/2}$, where $R_\mathrm{FC}\approx 6\,\um\gg\delta z$. However, in situations where $\delta z$ is a critical dimension (in the sense that increasing it would invalidate the physical model), one's only option is to decrease $\delta r$ by increasing the density of the mesh.

For this reason, mutli-layer structures with closely-spaced layers are the most challenging class of problem to solve. The iterative method used described in Section~\ref{section:model:multilayer} is memory-intensive for models with a large mesh (many vertices $p$ and triangles $t$, with typically $p\approx t / 2$) and/or many layers $L$, because the average distance between vertices decreases slowly with increasing number of triangles, $\langle\delta r\rangle\sim t^{-1/2}$, whereas the size of the (dense floating-point) $p\times t$ matrix that represents the dipole kernel $Q_z(\vec{r},\vec{r}')$ in Eq.~\ref{eq:hz-from-kernel} increases roughly as $t^2$. The end result is that the memory footprint of kernel matrix scales roughly as $\langle\delta r\rangle^{-4}$, so decreasing the mean distance between vertices by a factor of 2 increases the memory required by a factor of 16. Furthermore, for a model with $L$ layers there are $\binom{L}{2} = L(L-1)/2$ such kernel matrices needed for each iteration of the calculation outlined in Section~\ref{section:model:multilayer}. In \inline{superscreen.solve()}, these $\binom{L}{2}$ matrices are computed during the first iteration and then cached in memory for use in subsequent iterations. One can force the kernel matrices to be cached to disk if they would otherwise occupy too large a fraction of the available system memory using the \inline{cache_kernel_memory_cutoff} argument, but this comes at a significant performance cost.
